Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2022-06-11 doc/JFLA2022/Slides/Slides.tex
small changes to JFLA slides

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{The \Hydras project}
  \begin{block}{}
    \begin{itemize}
   \item Experimental platform for the  development of \textcolor{lookcolor}{maintained} and \textcolor{lookcolor}{documented} libraries of formal proofs.
    \item A project of \community, developped on GitHub
      \begin{itemize}
      \item CI/CD
        \item Tools for collaboration (issues, PR, etc.)
        \end{itemize}
      \item A book in PDF (300p), generated  with \textcolor{lookcolor}{\alectr} and \LaTeX, continuously updated and deployed
  \item          When appropriate, we present various proofs of the same statement, and interesting false starts.
    \end{itemize}
  \end{block}
  \begin{block}{Contents}
    \begin{itemize}
    \item Evolved version  of two contributions: \textcolor{plugincolor}{Cantor} and \textcolor{plugincolor}{Additions}
    \item Maintenance of \textcolor{plugincolor}{Ackermann}
      (part of Russel O'Connor's \textcolor{plugincolor}{Goedel})
    \item Bridge to \textcolor{plugincolor}{Gaia} (José Grimm) (\emph{in construction})

@@

 Cf.  \textcolor{pauillac}{Pauillac 2006} and \textcolor{banyuls}{Banyuls 2018}. Today, let us focus on some combinatorial aspects (number of rounds of a battle).
\end{frame}

@@

\only<2>{OK for large enough $i$ (K. \& S., 1981)}
\vspace{6pt}

@@

 Let us define \textcolor{mathcolor}{$H'_\alpha(i)$} as the least $l$ such that \textcolor{mathcolor}{$\alpha_l=0$} (Figure page.~\pageref{fig:accessibility}). 
 {\color{mathcolor}
\begin{align}
  H'_0(i) & = i\\
  H'_{\beta+1}(i) &=H'_\beta(i+1) \\
  H'_\lambda(i) &= H'_{(\canonseq{\lambda}{i+1})}(i)  \quad\textit{($\lambda$ limit ordinal)} 
\end{align}}

@@

    \item  Links with other representations of ordinals:

      \noindent
         Example (Minki Cho):
  \begin{scriptsize}
    {\color{blue}
\begin{verbatim}
Inductive Ord.t :=
| Ord.build: forall (A: Type), (A -> Ord.t) -> Ord.t.
\end{verbatim}
      }
 \end{scriptsize}

@@

  \begin{block}{}
  {\color{plugincolor}\Hydras} and  {\color{plugincolor}\community} are on GitHub. {\color{cyan}Please contribute, reuse!}
      \begin{itemize}
      \item New chapters
      \item Any correction or suggestion of improvement (text and/or proofs)

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{The \Hydras project}
  \begin{block}{}
    \begin{itemize}
    \item A project of \community:  experimental platform for the  development of
      \textcolor{lookcolor}{documented} and \textcolor{lookcolor}{maintained} libraries of formal proofs: 
    CI/CD,  Tools for collaboration (issues, PR, etc.)

  \item A book in PDF (300p), generated  with \textcolor{lookcolor}{\alectr} and \LaTeX, continuously updated and deployed.

    This book is structured around a few examples (algorithmics, ordinal numbers).
        When appropriate, various proofs of the same statement, and interesting false starts are presented.
    \end{itemize}
  \end{block}
  \begin{block}{Contents}
    \begin{itemize}
    \item Evolved version  of two contributions: \textcolor{plugincolor}{Cantor} and \textcolor{plugincolor}{Additions}
    \item Maintenance of \textcolor{plugincolor}{Ackermann}
      (part of Russel O'Connor's \textcolor{plugincolor}{Goedel})
    \item Bridge to \textcolor{plugincolor}{Gaia} (José Grimm) (\emph{in construction})

@@

 Cf.  \textcolor{pauillac}{Pauillac 2006} and \textcolor{banyuls}{Banyuls 2018}. Today, let us focus on some combinatorial aspects (\emph{e.g.} number of rounds of a battle).
\end{frame}

@@

\only<2>{{\color{lookcolor}OK for large enough $i$ (K. \& S., 1981)}}
\vspace{6pt}

@@

 {\color{mathcolor}
\begin{align}
  H'_0(i) & = i\\
  H'_{\beta+1}(i) &=H'_\beta(i+1) \\
  H'_\lambda(i) &= H'_{(\canonseq{\lambda}{i+1})}(i)  \quad\textit{($\lambda$ limit ordinal)} 
\end{align}}

\textcolor{mathcolor}{$H'_\alpha(i)$} is the least $l$ such that \textcolor{mathcolor}{$\alpha_l=0$} (cf. previous slide)).

@@

    \item  Links with other representations of ordinals, \emph{e.g.}:
  \begin{footnotesize}
    {\color{blue}
\begin{verbatim}
(* Minki Cho *)
Inductive Ord.t :=
| Ord.build: forall (A: Type), (A -> Ord.t) -> Ord.t.
\end{verbatim}
      }
 \end{footnotesize}

@@

  \begin{block}{}
  {\color{plugincolor}\Hydras} and  {\color{plugincolor}\community} are on GitHub. {\color{cyan}Please clone, fork, contribute!}
      \begin{itemize}
      \item New chapters
      \item Any correction or suggestion of improvement (text and/or proofs).
